% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Adam Watkins}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {engineering, soft errors},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}


% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  Los Alamos National Laboratory \\
  P.O. Box 1663  \\
  Los Alamos, NM 87545
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (217) 737-4933 \\
    Email: & \href{acwatkins88@lanl.gov}{\tt acwatkins88@lanl.gov} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
	
\item Ph.D. Electrical \& Computer Engineering, Southern Illinois University Carbondale, 2016 GPA: 3.769/4.0. 
\item M.S. Electrical \& Computer Engineering, Southern Illinois University Carbondale, 2012 GPA: 4.0/4.0.
\item B.S. Computer Engineering, Southern Illinois University Carbondale, 2010 GPA: 3.63/4.0.

\end{itemize}


\section*{Employment}

\begin{itemize}
\item Postdoctoral Research Associate, Los Alamos National Laboratory, December 2016--Present
\item Graduate Research Assistant, Los Alamos National Laboratory, May 2016--December 2016.
\item Doctorate Electrical Engineering Intern, Rockwell Collins, June 2015--August 2015.
\item Instructor, Southern Illinois University Carbondale, June 2011-May 2016
\item Research Assistant, Southern Illinois University Carbondale, August 2010--November 2016.
\end{itemize}


\section*{Publications}

\subsection*{Peer Reviewed}

\begin{itemize}

\item A. Watkins and S. Tragoudas, \emph{Radiation hardened latch designs for multi-node upsets}, IEEE Transactions on Emerging Topics in Computing \emph{Under Review}

\item A. Watkins and S. Tragoudas, \emph{METS: A multiple event transient simulator}, 2016 IEEE International Symposium on Circuits and Systems (ISCAS), Baltimore, MD, 2017. \emph{To Appear}
	
\item A. Watkins and S. Tragoudas, \emph{A highly robust double node upset tolerant latch}, 2016 IEEE International Symposium on Defect and Fault Tolerance in VLSI and Nanotechnology Systems (DFT), Storrs, CT, 2016.
	
\item A. Watkins and S. Tragoudas, \emph{An enhanced analytical electrical masking model for multiple event transients} In Proceedings of the 26th edition on Great Lakes Symposium on VLSI (GLSVLSI '16). ACM, New York, NY, 2016, pp. 369-372.
	
\item A. Watkins, V. Mudhireddy, H. Wang, and S. Tragoudas, \emph{Adaptive compressive sensing for low power wireless sensors}, In Proceedings of the 24th edition of the great lakes symposium on VLSI (GLSVLSI '14). ACM, New York, NY, 2014, pp. 99-104.

\item A. Watkins and S. Tragoudas, \emph{Transient pulse propagation using the Weibull distribution function}, 2012 IEEE International Symposium on Defect and Fault Tolerance in VLSI and Nanotechnology Systems (DFT), Austin, TX, 2012, pp. 109-114.
\end{itemize}

\subsection*{In Preparation}

\begin{itemize}
\item A. Watkins and S. Tragoudas, \emph{Fast and accurate simulation of multiple event transients}

\end{itemize}

\subsection*{Not Peer Reviewed}

\begin{itemize}
	\item A. Watkins, \emph{Analysis and mitigation of multiple radiation induced errors in modern circuits}, Ph.d. Dissertation
	
	\item A. Watkins, \emph{Radiation induced transient pulse propagation using the Weibull distribution function}, Master's Thesis
\end{itemize}

\subsection*{Patents}

\begin{itemize}
	\item A. Watkins and S. Tragoudas, \emph{A highly robust double node upset tolerant latch}, Provisional Patent 
\end{itemize}

\subsection*{Competitive Honors/Awards}

\begin{itemize}
	
	\item \emph{Best Student Paper Award}, DFT 2016
	\item \emph{ISR--3 Spot Award}, Los Alamos National Laboratory, 2016
	\item \emph{Outstanding Poster Award}, Los Alamos National Laboratory Student Symposium, 2016
	\item \emph{Heart of Illinois Waste Water Operators Scholarship}, 2008, \$500
	\item \emph{SIUC Dean Scholarship}, Southern Illinois University Carbondale, 2006, \$6000
	\item \emph{SIUC College of Engineering Scholarship}, Southern Illinois University Carbondale, 2006, \$1000
	
\end{itemize}

\subsection*{Professional Activities}

\begin{itemize}
	\item Reviewer: IOLTS 2017, IOLTS 2016, GLSVLSI 2016,  IEEE Transactions on Emerging Technologies in Computing 2016, ISQED 2016, GLSVLSI 2015, ISQED 2015, VLSI Design 2014, IOLTS 2012
	\item IEEE, Student Member, 2015-Present
\end{itemize}

\subsection*{Teaching Experience}

\begin{itemize}
	\item Fall 2015--Spring 2016, Instructor, ECE 296 Software Tools for Engineers
	\item Summer 2011--Fall 2015, Instructor, ECE 235 Electric Circuits
	\item Fall 2010--Spring 2011, Teaching Assistant, ECE 345 Electronic Devices

\end{itemize}

\end{document}
